---
title: "Swiss Abroad Parliament"
author: "Alexandra Kohler"
date: "27/06/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
library(rstudioapi)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
library(magrittr) # pipes
library(readxl) # excel
library(scales) # scales for ggplot2
library(jsonlite) # json
library(lintr) # code linting
library(sf) # spatial data handling
library(rgeos)
library(rgdal)
library(rmarkdown)
library(maps)
```

## Read in the data and prepare for analysis 


```{r parliament}

#-----------------------------
# READ IN PARLIAMENT DATA 

# set working directory
setwd("/Users/kohleralexandra/Documents/Projekte 2019/A_Wahlen 2019/Wahlprojekte/Auslandschweizer/scripts")
# read in data parl_ausl 
parlausl <- read.csv("/Users/kohleralexandra/Documents/Projekte 2019/A_Wahlen 2019/Wahlprojekte/Auslandschweizer/data/original_parl_ausl.csv", header = TRUE, fill = TRUE)

#----------------------------
# LOOK at data
head(parlausl)
summary(parlausl)
parlausl <- tbl_df(parlausl)
length(parlausl$firstname)
parlausl <- tbl_df(parlausl)
length(unique(parlausl$bill_id))
# Es gibt 3399 Zeilen, es gibt 16 bill ids und 17 vote-ids (Abstimmungen)
# Wir arbeiten mit den bill_ids

#----------------------------
# FILTER: pos_mp only "0 " and "1", call it parl_short. 
# we only look at approval and disapproval 
# from here, keep working with parl_short
# first unlist and then make numeric values instead of integers

parl_short <- parlausl %>%
  filter(position_mp == 0 | position_mp == 1)
length(parl_short$position_ASO)
length(unique(parl_short$firstname))
grüne <- parl_short %>% 
  filter(party_abbreviation == "GPS")

# Rename some of the parties 
parl_short %<>% 
  rename(
    FDP = "FDP-Liberale",
    CSP = "csp-ow",
    Grüne = "GPS",
    GLP = "glp"
  )



```

### Analyse data 

```{r parliament}


#----------------------------
# LOOK AT VOTE_IDs, count them and assign the categories 

colnames(parl_short)
length(unique(parl_short$vote_id))
length(unique(parl_short$bill_id))

# 16 unique bill-IDs
# 17 unique vote_ids
# BILL IDS: 15.3322 16.3219 15.4058 16.0450 16.0410 16.0270 15.4029 15.4142 17.3626 16.0710 18.3007 17.0460 16.0650 17.4710 18.4200 19.3294

# ADD CATEGORIES TO THE DATA 
# CATEGORIES: 4 Categories  "Uebrige", "E-Voting", "Interessen ASO", "Bankzugang"   
# Add the column category
# use case_when / ifelse to tell it which category to add to each row 

category <- c('Bankzugang', 'E-Voting', 'Interessen ASO', 'Medien', 'Uebrige')
length(category)

# Number of bills per category: 
# 3 Bankzugang
# 4 E-Voting
# 3 ASO-Interessen
# 2 Medien
# 4 Uebrige

# Assign the bil-id to the categories

parl_short %<>% mutate(category = case_when(
    vote_id == "50.13-17020" | vote_id == "50.8-15140" | vote_id == "50.10-15518" ~ "Bankzugang", 
    vote_id == "50.14-17362" | vote_id == "50.14-17363" | vote_id == "50.5-13865" |  
    vote_id == "50.18-19112" ~ "E-Voting", 
    vote_id == "50.10-15824" | vote_id == "50.13-17280" | vote_id == "50.6-14566" ~ "Interessen ASO", 
    vote_id == "50.6-14282" | vote_id == "50.6-14342"  ~ "Medien", 
    vote_id == "50.5-13808" | vote_id == "50.14-17330" | vote_id == "50.16-18222" |
    vote_id == "50.5-13868" | vote_id == "50.9-15371"  ~ "Uebrige",
    TRUE ~ "NA"
)) %>%
  # replace empty strings introduced by case_when to NA  
  mutate(category = ifelse(category == "NA", NA, category))


#Spot check
look_at_data <- parl_short %>% 
  filter(category == "Medien")
look_at_data
head(parl_short)
unique(look_at_data$date)

#----------------------------
# ADD VARIABLE POS_AGREED USING mutate()
# This Variable shows if the parliament agrees with the ASO - TrUE = yes, FALSE = no 
parl_short %<>% 
  mutate(pos_agreed = (position_mp == position_ASO))

# MAKE A SHORTER DATASET JUST TO LOOK AT THE CATEGORIZATION
parl_short_cat <- parl_short %>%
  select(vote_id, title_de, category) %>%
  group_by(vote_id)
head(parl_short_cat)

# WRITE CSV
write_csv(parl_short_cat, file = "parlament_auslandschweizer_voteids_categories.csv")

# ADD VARIABLE FULL_NAME USING unite()

parl_short %<>%
  unite(full_name, c("firstname", "lastname"), sep = " ", remove = FALSE) %>%
  # don't need these now anymore  
  select(-firstname, -lastname)

# SELECT the columns that you need 
parl_short %<>%
  select(vote_id, bill_id, title_de, date, full_name, party_abbreviation, position_ASO, position_mp, pos_agreed, category, yes_votes, no_votes, canton)



# beispiel hier https://tidyr.tidyverse.org/reference/unite.html oder hier https://stackoverflow.com/questions/50845474/concatenating-two-text-columns-in-dplyr 


#----------------------------
# WRITE CSV out
write.csv(parl_short, file = "parlament_auslandschweizer_votings_categories.csv", fileEncoding ="UTF-8")

```

## ANALYSIS 2: FIND OUT OVERALL, PARITES, POLITICIANS THAT AGREE THE MOST AND PER CATEGORY 

PARTIES
overall 1677 agreed, 1216 disagreed
SVP 129 agreed, 821 disagreed
SP 625 agreed, 13 disagreed
Gruene 139 agreed, 24 disagreed
FDP 
CVP

```{r}

# PARTIES 
parties <- parl_short %>% 
  group_by(party_abbreviation) %>% 
  summarise(
    n_agreed = sum(pos_agreed, na.rm = TRUE),
    n_disagreed = sum(pos_agreed == FALSE, na.rm = TRUE) 
  ) %>%
  # calculate ratio of agrees / disagrees
  mutate(share_agreed = n_agreed / (n_agreed + n_disagreed))  %>% 
  arrange(desc(share_agreed)) %>% 
  mutate(share_percent = share_agreed * 100) %>% 
  mutate(share__no_percent = 100 - share_percent)

parl_short %<>% 
  mutate(n_pos_agreed = sum(pos_agreed = TRUE))
parl_short %<>% 
  mutate(n_pos_disagreed = sum(pos_agreed = FALSE))


# PERSONS: 225 Personen 

persons_rank <- parl_short %>% 
  group_by(full_name, party_abbreviation) %>% 
  # create sums of all agrees and disagrees per parliamentarian
  summarise(
    n_agreed = sum(pos_agreed, na.rm = TRUE),
    n_disagreed = sum(pos_agreed == FALSE, na.rm = TRUE) 
  ) %>%
  # calculate ratio of agrees / disagrees
  mutate(share_agreed = n_agreed / (n_agreed + n_disagreed))  %>% 
  arrange(desc(share_agreed))
# Overall, the people that were the most Auslandschweizer friendly, are: Barbara Gysi, Claudia Friedl, Edith Graf-Litscher, Mathias Aebischer


# CATEGORIES: 4 Categories  "Uebrige", "E-Voting", "Interessen ASO", "Bankzugang"    
# Overall, the people that were the most Auslandschweizer friendly, are: Barbara Gysi, Claudia Friedl, Edith Graf-Litscher, Mathias Aebischer

categories_rank <- parl_short %>% 
  group_by(category, party_abbreviation) %>% 
  # create sums of all agrees and disagrees per parliamentarian
  summarise(
    n_agreed = sum(pos_agreed, na.rm = TRUE),
    n_disagreed = sum(pos_agreed == FALSE, na.rm = TRUE) 
  ) %>%
  # calculate ratio of agrees / disagrees
  mutate(share_agreed = n_agreed / (n_agreed + n_disagreed))  %>% 
  mutate(share_percent = share_agreed * 100) %>% 
  mutate(share_no_percent = 100 - share_percent)  %>% 
  arrange(desc(share_agreed))
unique(categories_rank$category)

# WRITE CSV ou
write.csv(categories_rank, file = "parties_evaluation_categories.csv", fileEncoding ="UTF-8")

## Filter nur Bankenzugang
Banken <- categories_rank %>% 
  filter(category == "Bankzugang")

## Filter nur Medien
Medien <- categories_rank %>% 
  filter(category == "Medien")

# Filter nur ASO Interessen
ASO <- categories_rank %>% 
  filter(category == "Interessen ASO")


# Filter nur E-Voting
Evoting <- categories_rank %>% 
  filter(category == "E-Voting")


# Filter nur Uebrige
Uebrige <- categories_rank %>% 
  filter(category == "Uebrige")